### 2018-03-28 Sections/classical_networking_protocols.tex
Latin quotes done
Quantum simulation complete
CV figs, sec

%
% Internet Protocol (IP)
%

\subsubsection{Internet Protocol (IP)} \index{Internet Protocol (IP)}

@@

%
% User Datagram Protocol (UDP)
%

\subsubsection{User Datagram Protocol (UDP)} \index{User Datagram Protocol (UDP)}

@@

\subsubsection{Transmission Control Protocol (TCP)} \label{sec:TCP} \index{Transmission Control Protocol (TCP)}

>>>>

%
% Internet Protocol
%

\subsubsection{Internet Protocol} \index{Internet Protocol}

@@

%
% User Datagram Protocol
%

\subsubsection{User Datagram Protocol} \index{User Datagram Protocol}

@@

\subsubsection{Transmission Control Protocol} \label{sec:TCP} \index{Transmission Control Protocol}

### 2018-03-28 Sections/cryptowars.tex
CV figs, sec

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function DigitalSignature(message,keyPair):
\begin{enumerate}
\item Alice prepares a short \textit{digest}\index{Digest} of her message using a cryptographic hash function\index{Hash function}, such as SHA256\index{SHA256} (Sec.~\ref{sec:hashing}),\\
	\vspace{1mm} 
	$\text{digest=SHA256(message)}$
	\item Alice encrypts the digest using her private key. This forms the `digital signature',\\
	\vspace{1mm} 
	$\text{signature = RSAEncrypt(digest,privateKey)}$
	\item Alice transmits the digital signature and original message to Bob,\\
	\vspace{1mm} 
	$\text{signedMessage = \{message,signature\}}$
	\item Bob hashes the received message,\\
	\vspace{1mm} 	
	$\text{hash=SHA256(message)}$
	\item Bob uses Alice's public-key to decrypt her digital signature,\\
	\vspace{1mm} 
	$\text{decryptedHash = RSADecrypt(signature,publicKey)}$
	\item Bob compares his calculated hash with Alice's decrypted hash for consistency. If the two hashes are identical, Bob concludes the message was authentic,\\
	\vspace{1mm} 
	$\text{if(decryptedHash=hash)}$\\
	$\,\,\text{return(pass)}$\\
	$\text{else}$\\
	$\,\,\text{return(fail)}$
	\item $\Box$
\end{enumerate}
}}}
\caption{Protocol for digitally signing a message using public-key cryptography (RSA) and a cryptographic hash function (SHA256).} \label{alg:dig_sig}
\end{table}

@@

\subsubsection{Quantum key distribution (QKD)} \label{sec:QKD} \index{Quantum key distribution (QKD)}

@@

\comment{Add more advanced protocols? CV? Decoy states, untrusted devices, device independent QKD, etc. etc.}

@@

QKD is a relatively mature technology with already several commercial systems being available off-the-shelf\footnote{\cite{??? example companies}} and initial space-based implementations have been successfully demonstrated \cite{Pan}.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function BB84():
\begin{enumerate}
\item Alice chooses a random bit, $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\end{enumerate}}}}
\caption{BB84\index{BB84 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string for use in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:bb84}
\end{table}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function E91():
\begin{enumerate}
\item A central server shares a Bell-pair between Alice and Bob,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
\item Alice randomly measures her qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Bob randomly measures his qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Alice and Bob share what their measurement bases were (classically and unencrypted).
\item When Alice and Bob's bases were consistent they store the measurement outcomes as a shared random bit.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\end{enumerate}}}}
\caption{E91\index{E91 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photonic Bell-pairs. Upon completion of the protocol, Alice and Bob share a random bit-string of ruse in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:e91}
\end{table}

@@

\paragraph{Continuous-variable protocols}

\comment{To do. Zixin perhaps??}

>>>>

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function DigitalSignature(message,keyPair):
\begin{enumerate}
\item Alice prepares a short \textit{digest}\index{Digest} of her message using a cryptographic hash function\index{Hash function}, such as SHA256\index{SHA256} (Sec.~\ref{sec:hashing}),\\
	\vspace{1mm} 
	$digest=SHA256(message)$
	\item Alice encrypts the digest using her private key. This forms the `digital signature',\\
	\vspace{1mm} 
	$signature = RSAEncrypt(digest,privateKey)$
	\item Alice transmits the digital signature and original message to Bob,\\
	\vspace{1mm} 
	$signedMessage = \{message,signature\}$
	\item Bob hashes the received message,\\
	\vspace{1mm} 	
	$hash=SHA256(message)$
	\item Bob uses Alice's public-key to decrypt her digital signature,\\
	\vspace{1mm} 
	$decryptedHash =$\\
	$RSADecrypt(signature,publicKey)$
	\item Bob compares his calculated hash with Alice's decrypted hash for consistency. If the two hashes are identical, Bob concludes the message was authentic,\\
	\vspace{1mm} 
	$if(decryptedHash=hash)$\\
	$\,\,return(pass)$\\
	$else$\\
	$\,\,return(fail)$
	\item $\Box$
\end{enumerate}
}}}
\caption{Protocol for digitally signing a message using public-key cryptography (RSA) and a cryptographic hash function (SHA256).} \label{alg:dig_sig}
\end{table}

@@

\subsubsection{Quantum key distribution} \label{sec:QKD} \index{Quantum key distribution}

@@

\comment{Add more advanced protocols? Decoy states, untrusted devices, device independent QKD, etc. etc.}

@@

QKD is a relatively mature technology with already several commercial systems being available off-the-shelf\footnote{Examples of companies selling off-the-shelf QKD hardware include \href{http://www.magiqtech.com}{MagiQ} and \href{http://www.idquantique.com}{ID Quantique}.} and initial space-based implementations have been successfully demonstrated \cite{Pan}.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function BB84():
\begin{enumerate}
\item Alice chooses a random bit, $0$ or $1$.
\item Alice randomly chooses a basis, $\hat{X}$ or $\hat{Z}$.
\item Depending on the choice of basis, she encodes her bit into the polarisation of a single photon as:
\begin{align}
\ket{0}_Z &\equiv \ket{H}, \nonumber \\
\ket{1}_Z &\equiv \ket{V},
\end{align}
or,
\begin{align}
\ket{0}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}+\ket{V}), \nonumber \\
\ket{1}_X &\equiv \frac{1}{\sqrt{2}}(\ket{H}-\ket{V}).
\end{align}
\item Encoding into the randomly chosen basis, she transmits the randomly chosen bit to Bob.
\item She does not announce the choice of bit or basis.
\item Bob measures the bit in a randomly chosen basis, $\hat{X}$ or $\hat{Z}$.
\item The above is repeated many times.
\item Upon receipt of all qubits, Alice (publicly) announces the basis used for encoding each bit sent.
\item Qubits where Bob measured in the opposite basis to which Alice encoded are discarded, as they will be decorrelated from Alice.
\item The remaining measurement outcomes are guaranteed to yield identical bits between Alice and Bob.
\item Remaining is roughly half as many bits as were sent, which are random, but guaranteed to be identical between Alice and Bob.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}}}
\caption{BB84\index{BB84 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photons. Upon completion of the protocol, Alice and Bob share a random bit-string for use in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:bb84}
\end{table}

@@

\comment{Fix this up. Discuss using Bell violation to prove security.}

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function E91():
\begin{enumerate}
\item A central server shares a Bell-pair between Alice and Bob,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B+\ket{1}_A\ket{1}_B).
\end{align}
\item Alice randomly measures her qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Bob randomly measures his qubit in either the $\hat{X}$ or $\hat{Z}$ basis.
\item Alice and Bob share what their measurement bases were (classically and unencrypted).
\item When Alice and Bob's bases were consistent they store the measurement outcomes as a shared random bit.
\item Alice and Bob sacrifice some of their bits by publicly communicating them to check for consistency. This rules out intercept-resend attacks.
\item Privacy amplification may be used to distill the partially compromised key into a shorter but more secret one.
\item $\Box$
\end{enumerate}}}}
\caption{E91\index{E91 protocol} QKD protocol using polarisation-encoded\index{Polarisation encoding} photonic Bell-pairs. Upon completion of the protocol, Alice and Bob share a random bit-string of ruse in a one-time pad cipher\index{One-time pad cipher}.}\label{alg:e91}
\end{table}

@@

\paragraph{Continuous-variable protocols}\index{Continuous-variable QKD}

Like quantum computing, QKD protocols may be adapted to the CV domain also. Alg.~\ref{alg:cv_qkd} describes a simple such scheme based on encoding in phase-space\index{Phase-space}, where the basis states are coherent states of different amplitudes and phases. The goal is the same as BB84 -- to securely share a random bit-string for use in a one-time-pad\index{One-time-pad}.

Note that this protocol provides information-theoretic security\index{Information-theoretic security}, as per BB84\index{BB84 protocol}, despite the fact that coherent states are non-orthogonal, forming an over-complete basis in phase-space.

Conceptually, the operation of the CV QKD protocol is virtually identical to photonic BB84, differing only in that now the different choices of encodings correspond to phase-space transformations. Like BB84, if Eve were to perform an intercept-resend attack\index{Intercept-resend attack} she would probabilistically re-encode in the wrong quadrature, thereby revealing herself to Alice and Bob, who could then terminate.

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function CVQKD():
\begin{enumerate}
\item Alice two Gaussian-distributed random numbers with mean zero,
\begin{align}
x_A &= \mathcal{N}(0,V_\text{mod}),\nonumber \\
p_A &= \mathcal{N}(0,V_\text{mod}),
\end{align}
where $V_\text{mod}$ is the modulation variance\index{Modulation variance}.
\item Alice prepares the coherent state,
\begin{align}
\ket\alpha = \ket{x_A+ip_A}.	
\end{align}
\item Alice transmits $\ket\alpha$ to Bob.
\item Bob randomly measures either $\hat{x}$ or $\hat{p}$ using homodyne detection.
\item Alice and Bob use classical communication to determine for which transmissions their preparation and measurement were consistent \comment{I don't get this, Alice is deterministically encoding x+ip, where's the randomness in the choice of basis? Are we adding a randomised phase that puts us into a diagonal basis sometimes, or something like that}
\item \comment{Complete the rest of this}
\end{enumerate}}}}
\caption{CV QKD protocol using coherent states, encoded in the quadrature basis.}\label{alg:cv_qkd}
\end{table}

\comment{To do.}

### 2018-03-28 Sections/economics_of_the_quantum_internet.tex
CV figs, sec

Let,
\begin{align}
	0\leq r_n \leq 1,
\end{align}
be the proportion of compute-time allocated to a node in possession of $n$ qubits, in a global network of $n_\text{global}$ qubits. Arbitrage in the value of physical qubits will enforce the linearity constraint,
\begin{align}
	r_{n_1+n_2} = r_{n_1} + r_{n_2}.
\end{align}
This constraint effectively mandates that `all qubits are created equal', and two qubits are twice as valuable as one -- \textit{Qubit aequalitatem}. Were, for example, a bundle of two qubits more expensive than two individual qubits purchased in isolation, a market participant could perform arbitrage and unfairly gain free compute-time by buying two qubits separately, unifying them, selling the bundle, buying them back individually, and repeating indefinitely until he seizes the entire network.

>>>>

Let,
\begin{align}
	0\leq r_n \leq 1,
\end{align}
be the proportion of compute-time allocated to a node in possession of $n$ qubits, in a global network of $n_\text{global}$ qubits. Arbitrage in the value of physical qubits will enforce the linearity constraint,
\begin{align}
	r_{n_1+n_2} = r_{n_1} + r_{n_2}.
\end{align}
This constraint effectively mandates that `all qubits are created equal', and two qubits are twice as valuable as one \latinquote{Qubit aequalitatem}. Were, for example, a bundle of two qubits more expensive than two individual qubits purchased in isolation, a market participant could perform arbitrage and unfairly gain free compute-time by buying two qubits separately, unifying them, selling the bundle, buying them back individually, and repeating indefinitely until he seizes the entire network.

### 2018-03-28 Sections/network_topologies.tex
Latin quote stubs
Latin quotes done
CV figs, sec

We will now review some of the graph structures most likely to arise in quantum networks.

@@

\subsection{Point-to-point (P2P)} \index{Point-to-point (P2P) topologies}

>>>>

We will now review some of the graph structures most likely to arise in quantum networks, learning from the structures that have become ubiquitous in classical networking.

@@

\subsection{Point-to-point} \index{Point-to-point topologies}

### 2018-03-28 Sections/physical_architectures_for_quantum_computing.tex
CV figs, sec

%
% Continuous-Variables (CV)
%

\subsection{Continuous-variables (CV)} \label{sec:CV_QC} \index{Continuous-variable quantum computation}

@@

In the CV picture, instead of representing states using photonic creation operators ($\hat a^\dag$), we express them in terms of the \textit{position} ($\hat x$)\index{Position operator} and \textit{momentum} ($\hat p$)\index{Momentum operator} operators, which can expressed in terms of creation and annihilation operators as,
\begin{align}
\hat x &=    \sqrt{\frac{\hbar}{2 \omega}}(\hat a + \hat a^\dag), \nonumber \\
\hat p &= -i \sqrt{\frac{\hbar  \omega}{2}}(\hat a - \hat a^\dag), 
\end{align}
where $\omega$ is the optical frequency. These operators obey the commutation relation,
\begin{align}
[\hat x, \hat p] = i \hbar.
\end{align}

@@

The position representation corresponds to expressing a state vector $\ket{\psi}$ in the position basis\index{Position basis representation},
\begin{align}
\ket{\psi} = \int \psi(x)\ket{x}\, dx,
\end{align}
\noindent where $\ket{x}$ are the eigenstates of the position operator. Here the wave function in the position representation is defined as,
\begin{align}
\psi(x) = \langle x|\psi\rangle.
\end{align}
The state can similarly be expressed in the momentum basis.\index{Momentum basis representation}

The quadrature eigenstates are mutually related to each other by a Fourier transform,
\begin{align}
\ket{x} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{-2 i x p} \ket{p} \,dp,\nonumber \\
\ket{p} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{+2 i x p} \ket{x} \,dx.
\end{align}

Position and momentum eigenstates are orthogonal and may therefore be employed to encode a single qubit. However, these eigenstates have infinite energy. That is, they are infinitely squeezed in phase-space (Sec.~\ref{sec:squeezed},\ref{sec:non_lin_opt}). However, position and momentum eigenstates can be closely approximated using finite, but large squeezing. The squeezed states\index{Squeezed states} in the two quadratures will now no longer be orthogonal, but will have overlap that asymptotes to zero as squeezing is increased. Thus, squeezed states can be used to approximate qubits using non-orthogonal basis states. Squeezed states may be prepared directly using a spontaneous parametric down-conversion (SPDC)\index{Spontaneous parametric down-conversion} process (Sec.~\ref{sec:single_phot_src}) \cite{bib:PhysRevLett.75.4337, bib:o2009photonic}.

Squeezing simply corresponds to a dilation along a particular axis in phase-space. Squeezing is represented using the squeezing operator\index{Squeezing operator},
\begin{align}\label{eq:sq_op}
\hat{S}(\xi) = \text{exp}\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where \mbox{$\xi  = r e^{i \varphi}$}, $r$ is known as the squeezing parameter, which will determine the size of the squeezing and \mbox{$\varphi \in [0, 2\pi]$} denotes that axis along which the squeezing is taking place.

A phase-shifter\index{Phase-shifter}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat a^\dag \hat a},
\end{align}
rotates a state in phase-space by angle $\theta$, implementing the transformation between the position and momentum operators,
\begin{align}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in the position/momentum basis.

Measurement of CV states may be performed using homodyne detection\index{Homodyne detection} (Sec.~\ref{sec:homodyne}), which perform a projection along some axis in phase-space, allowing $\hat{x}$ and $\hat{p}$, or any linear combination of the two, to be directly sampled.

@@

A full set of circuit model CV gates, universal for CV quantum computing is summarised in Table.~\ref{tab:CV_gates} \cite{bib:RevModPhys.84.621}.
\begin{table}[!htb]
\begin{tabular}{ |c|c| } 
 \hline
 Qubit model gate &  CV equivalent \\ 
  \hline\hline
 Pauli $X$ & $\hat{X}(s) = \exp[-i s \hat p]$  \\ 
 Pauli $Z$ & $\hat{Z}(t) = \exp[i t \hat q]$  \\ 
 Phase gate & $\hat{P}(\eta) = \exp[i \eta \hat x^2]$ \\
Hadamard   & $\hat{F}=\exp[i \frac{\pi}{8}(\hat p^2+\hat q^2)]$ \\
CZ		   & $\hat{U}_\text{CZ}= \exp[\frac{i}{2}\hat q_1 \hat q_2]$ \\
CNOT 	   & $\hat{U}_\text{CNOT} = \exp[-2i\hat x_1 \hat p_2]$\\
\hline
\end{tabular}
\caption{Logical generalisations of a universal gate set to the CV model for quantum computing.\label{tab:CV_gates}}
\end{table}

>>>>

%
% Continuous-Variables
%

\subsection{Continuous-variables} \label{sec:CV_QC} \index{Continuous-variable quantum computation}

@@

In the CV picture, instead of representing states using photonic creation operators ($\hat a^\dag$), we express them in terms of the \textit{position} ($\hat x$)\index{Position operator} and \textit{momentum} ($\hat p$)\index{Momentum operator} operators, which can expressed in terms of creation and annihilation operators as,
\begin{align}
\hat x &=    \sqrt{\frac{\hbar}{2 \omega}}(\hat a + \hat a^\dag), \nonumber \\
\hat p &= -i \sqrt{\frac{\hbar  \omega}{2}}(\hat a - \hat a^\dag), 
\end{align}
where $\omega$ is the optical frequency\index{Optical frequency}. These operators obey the commutation relation,
\begin{align}
[\hat x, \hat p] = i \hbar.
\end{align}

@@

The position representation corresponds to expressing a state vector $\ket{\psi}$ in the position basis\index{Position basis representation},
\begin{align}
\ket{\psi} = \int \psi(x)\ket{x}\, dx,
\end{align}
\noindent where $\ket{x}$ are the eigenstates of the position operator. Here the wave function in the position representation\index{Position basis representation} is defined as,
\begin{align}
\psi(x) = \langle x|\psi\rangle.
\end{align}
The state can similarly be expressed in the momentum basis.\index{Momentum basis representation}

The quadrature eigenstates\index{Quadrature eigenstates} are mutually related to each other by a Fourier transform\index{Fourier transform},
\begin{align}
\ket{x} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{-2 i x p} \ket{p} \,dp,\nonumber \\
\ket{p} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{+2 i x p} \ket{x} \,dx.
\end{align}

%
% Encoding Quantum Information Using Squeezed States
%

\subsubsection{Encoding quantum information using squeezed state}\index{Squeezed state encoding}

Position and momentum eigenstates are orthogonal and may therefore be employed to encode a single qubit. However, these eigenstates have infinite energy. That is, they are infinitely squeezed in phase-space (Sec.~\ref{sec:squeezed}, \ref{sec:non_lin_opt})\index{Infinite squeezing}. However, position and momentum eigenstates can be closely approximated using finite, but large squeezing. The squeezed states\index{Squeezed states} in the two quadratures will now no longer be orthogonal, but will have overlap that asymptotes to zero as squeezing is increased. Thus, squeezed states can be used to approximate qubits using non-orthogonal basis states. Squeezed states may be prepared directly using a spontaneous parametric down-conversion (SPDC)\index{Spontaneous parametric down-conversion} process (Sec.~\ref{sec:single_phot_src}) \cite{bib:PhysRevLett.75.4337, bib:o2009photonic}. CV encoding using squeezed states is illustrated in phase-space in Fig.~\ref{fig:squeezed_state_encoding}.

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{squeezed_state_encoding}
\caption{Phase-space representation of two squeezed vacuum states, squeezed in the $\hat{x}$ (blue) and $\hat{p}$ (red) directions. In the limit of large squeezing these states become approximately orthogonal and may therefore approximate the encoding of a qubit.} \label{fig:squeezed_state_encoding}	
\end{figure}

Squeezing simply corresponds to a dilation along a particular axis in phase-space. Squeezing is represented using the squeezing operator\index{Squeezing operator},
\begin{align}\label{eq:sq_op}
\hat{S}(\xi) = \text{exp}\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where \mbox{$\xi  = r e^{i \varphi}$}, $r$ is known as the squeezing parameter\index{Squeezing parameter}, which will determine the size of the squeezing and \mbox{$\varphi \in [0, 2\pi]$} denotes that axis along which the squeezing is taking place.

\comment{How is squeezing implemented physically in the lab?}

%
% Phase-Shifters
%

\subsubsection{Phase-shifters}\index{Phase-shifters}

A phase-shifter\index{Phase-shifters}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat a^\dag \hat a},
\end{align}
rotates a state in phase-space by angle $\theta$, implementing the transformation between the position and momentum operators,
\begin{align}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in the position/momentum basis. \comment{Is it right that this is a single qubit operation in the x/p basis?}

%
% Bell-Pairs
%

\subsubsection{Bell-pairs}\index{Bell-pairs}\label{sec:CV_bell_pairs}

In the squeezed basis one can prepare Bell-pairs in an analogous manner to doing so using single-photon encoding. Namely, mixing two orthogonally squeezed states (squeezed and anti-squeezed states) on a 50:50 beamsplitter generates Bell-type entanglement. This is shown in Fig.~\ref{fig:CV_bell_pair}.

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{CV_bell_pair}
\caption{Preparation of a CV Bell-pair using a 50:50 beamsplitter to entangled two  squeezed states, squeezed in orthogonal directions in phase-space.}\label{fig:CV_bell_pair}	
\end{figure}

\comment{This is deterministic?}

%
% Measurement
%

\subsubsection{Measurement}

Measurement of CV states may be performed using homodyne detection\index{Homodyne detection} (Sec.~\ref{sec:homodyne}), which perform a projection along an arbitrary axis in phase-space, allowing $\hat{x}$ and $\hat{p}$, or any linear combination of the two, to be directly sampled.

Using a 50:50 beamsplitter to implement the reverse of Bell-pair preparation (described previously in Sec.~\ref{sec:CV_bell_pairs}), one can construct a Bell analyser for performing projections in the Bell basis\index{Bell projections}.

\comment{Is this right?}

\comment{Can we distinguish all 4 Bell states, or just 2 like LOQC?}

%
% Logical Operations
%

\subsubsection{Logical operations}

@@

A full set of circuit model CV gates, universal for CV quantum computing is summarised in Table.~\ref{tab:CV_gates} \cite{bib:RevModPhys.84.621}.
\begin{table}[!htb]
\begin{tabular}{ |c|c| } 
 \hline
 Qubit model gate &  CV equivalent \\ 
  \hline\hline
 Pauli $X$ & $\hat{X}(s) = \exp[-i s \hat p]$  \\ 
 Pauli $Z$ & $\hat{Z}(t) = \exp[i t \hat x]$  \\ 
 Phase gate & $\hat{P}(\eta) = \exp[i \eta \hat x^2]$ \\
Hadamard   & $\hat{F}=\exp[i \frac{\pi}{8}(\hat p^2+\hat x^2)]$ \\
CZ		   & $\hat{U}_\text{CZ}= \exp[\frac{i}{2}\hat x_1 \hat x_2]$ \\
CNOT 	   & $\hat{U}_\text{CNOT} = \exp[-2i\hat x_1 \hat p_2]$\\
\hline
\end{tabular}
\caption{Logical generalisations of a universal gate set to the CV model for quantum computing.\label{tab:CV_gates}}
\end{table}

\comment{Here explicitly show construction of a CZ gate.}

\comment{Reference to work by Menicucci on fault tolerant implementation of CV QC.}

%
% Cluster States
%

\subsubsection{Cluster states}

\comment{Describe the basic building blocks in a squeezed state cluster state architecture}

\comment{Please add any citations necessary for this entire section. Both theory and experimental work.}

### 2018-03-28 Sections/protocols_for_the_quantum_internet.tex
CV figs, sec

A homodyne detector interferes a state with a coherent state on a beamsplitter, which acts as a phase-reference, before photo-detecting both output modes and taking the difference in the photon count-rates (Fig.~\ref{fig:homodyne}).

By sweeping through the amplitude and phase of the reference beam, we are able to directly sample points in phase-space, allowing the Wigner function -- which is isomorphic to the density operator -- of an unknown state to be fully reconstructed.

@@

@@

%
% Quantum non-demolition measurement (QND)
%

\subsubsection{Quantum non-demolition measurement (QND)}\index{Quantum non-demolition measurement (QND)}

@@

>>>>

A homodyne detector interferes a state with a coherent state on a beamsplitter, which acts as a phase-reference\index{Phase-reference}, before photo-detecting both output modes and taking the difference in the photon count-rates (Fig.~\ref{fig:homodyne}).

By sweeping through the amplitude and phase of the reference beam, we are able to directly sample points in phase-space, allowing the Wigner function\index{Wigner function} -- which is isomorphic to the density operator -- of an unknown state to be fully reconstructed.

@@

The operation of homodyne measurement is most easily visualised in phase-space, where it can be regarded as integrating along an infinite line with arbitrary rotation determined by the phase-reference.

@@

%
% Quantum non-demolition measurement
%

\subsubsection{Quantum non-demolition measurement}\index{Quantum non-demolition measurement}

\comment{To do! List abbrev.}

@@

\comment{Need to reference figure}

### 2018-03-28 Sections/quality_of_service.tex
CV figs, sec

\section{Quality of service (QoS)}\index{Quantum error correction (QEC)}\index{Quality of service}\label{sec:QOS_chap}

@@

%
% Continuous-Variable Quantum Error Correction
%

\subsection{Continuous-variable quantum error correction}\index{Continuous-variable quantum error correction}

>>>>

\section{Quality of service}\index{Quantum error correction}\index{Quality of service}\label{sec:QOS_chap}

@@

%
% Continuous-Variables
%

\subsection{Continuous-variables}\index{Continuous-variable quantum error correction}

First CV QEC protocol is the direct analogue of the the qubit redundancy codes. However, the noise models do not correspond to what usually occur in Gaussian systems, namely, thermal noise\index{Thermal noise} and loss.

It has been proven that QEC of Gaussian noise on Gaussian states, using only Gaussian operations is impossible \cite{bib:PhysRevLett.102.120501}. It is closely related to entanglement distillation, discusses above. Several approaches have since been developed. One proposes to encode information in non-Gaussian CV states, then error correction can be implemented using Gaussian operations, resulting in a Gaussian state \cite{bib:pirandola2004constructing}. Another approach is to error correct on Gaussian states using non-Gaussian operations, similar to the entanglement distillation protocol. It is unclear which one is the most advantageous.

\comment{To do -- can we be a bit more specific about the physical resource requirements and the specific noise models? Specify what Gaussian noise means.}
